The K2 Bright Star Survey

### 2019-05-09 paper/ms.tex

\begin{figure*}
\plotone{lag_opt_both.pdf}
\caption{Behaviour of long cadence 6.5~hour CDPP (bottom) and $4 c/d$ systematics power (top) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$. CDPP shows a minimum for L1 norm and $\delta=10$, i.e. for objective function $Q_{1,10}$.}
\label{cdpps}
\end{figure*}

>>>>

\begin{figure*}
\plotone{lag_opt_both.pdf}
\caption{Behaviour of long cadence 6.5~hour CDPP (bottom) and $4 c/d$ systematics power (top) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$. CDPP shows a minimum for L1 norm and $\delta=10$, i.e. for objective function $Q_{1,10}$, which is marked with a blue dashed vertical line. This does not correspond to an optimum in systematic power, which is slightly lower for smaller $\delta$. Nevertheless, we have chosen $\delta=10$ for the light curves in this catalog because of its improvement in overall CDPP as a measure of planet detection efficiency and overall light curve quality.}
\label{cdpps}
\end{figure*}
